Fast gravitational wave parameter estimation without compromises

### 2023-08-07 src/tex/ms.tex
Update

% Old codes have trouble handling next gen data
% The PE results in the most recent catalog of GW events are produced by several
% community-developed PE codes
% \mi{what catalog do you mean? The LVK doesn't use PyCBC Inference}
There exist a number of prominent, community-developed PE codes, including
\textsc{LALInference} \citep{Veitch:2014wba}, \textsc{PyCBC Inference}
\citep{Biwer:2018osg}, and \textsc{Bilby}
\citep{Ashton:2018jfp,Romero-Shaw:2020owr}.  These packages have been tested by a
number of groups and are well regarded as standard tools. However, while these
tools have passed many robustness tests, they are known to be computationally
intensive. The exact amount of time needed to analyze one event depends on
factors like the duration and frequency of the signal, as well as features of
the specific waveform model. Typical runtimes for production-level analyses can
range from hours to weeks.
This expense precludes iterating quickly on results,
launching large scale measurement simulations, or obtaining final parameter estimates in low
latency to inform astronomers for potential followup in real time.%
\footnote{\corr{Although approximate skymaps can currently be produced in low latency, the same is not true 
of final estimate of other parameters, like masses and spins, which may inform the probability of electromagnetic emission
 followup strategy and thus affect followup strategy.}}

>>>>

% Old codes have trouble handling next gen data
% The PE results in the most recent catalog of GW events are produced by several
% community-developed PE codes
% \mi{what catalog do you mean? The LVK doesn't use PyCBC Inference}
There exist a number of prominent, community-developed PE codes, including
\textsc{LALInference} \citep{Veitch:2014wba}, \textsc{PyCBC Inference}
\citep{Biwer:2018osg}, and \textsc{Bilby}
\citep{Ashton:2018jfp,Romero-Shaw:2020owr}.  These packages have been tested by a
number of groups and are well regarded as standard tools. However, while these
tools have passed many robustness tests, they are known to be computationally
intensive. The exact amount of time needed to analyze one event depends on
factors like the duration and frequency of the signal, as well as features of
the specific waveform model. Typical runtimes for production-level analyses can
range from hours to weeks.
This expense precludes iterating quickly on results,
launching large scale measurement simulations, or \corr{obtaining final parameter estimates} in low
latency to inform astronomers for potential followup in real time.%
\footnote{\corr{Although approximate skymaps can currently be produced in low latency, the same is not true 
of final estimate of other parameters, like masses and spins, which may inform the probability of electromagnetic emission
 followup strategy and thus affect followup strategy.}}
